\documentclass[14pt]{article}

% Packages
\usepackage{ezra}

% Title
\title{2004 C1}
\author{Ezra Guerrero Alvarez}

% Formatting
\setlength{\parindent}{0pt}

%document
\begin{document}
\maketitle
	
\section*{2004 C1}

\begin{statement}{2004 C1}
	There are $10001$ students at an university. Some students 
	join together to form several clubs (a student may belong to 
	different clubs). Some clubs join together to form several 
	societies (a club may belong to different societies). There 
	are a total of $k$ societies. Suppose that the following 
	conditions hold:
	\begin{enumerate}
		\item Each pair of students are in exactly one club.
		\item For each student and each society, the student is 
		in exactly one club of the society.
		\item Each club has an odd number of students. In 
		addition, a club with ${2m+1}$ students ($m$ is a 
		positive integer) is in exactly $m$ societies.
	\end{enumerate}
	Find all possible values of $k$.
\end{statement}
The only possible $k$ is $5000$. Indeed, replace $10001$ by 
$2K+1$, we prove the only possible $k$ is $K$. First, note that 
$K$ is achievable by taking one club with every student in it 
that belongs to $K$ societies. This satisfies every condition. 
Now, we prove $k$ can only be $K$. Indeed, suppose there are 
$2c_i+1$ students in club $i$. The first condition guarantees 
that $\binom{2K+1}2=\sum\binom{2c_i+1}2$, or 
\[ K(2K+1)=\sum c_i(2c_i+1). \]
Now, from the second condition it is clear every student is in 
exactly $k$ societies. Thus, if we add the number of students in 
each society we obtain $k(2K+1)$. The second condition also 
gives that, within a society, each pair of clubs is disjoint. 
Hence, the number of students in a given society is the sum of 
the number of students in each club in the society. Summing over 
all societies, each club gets counted $c_i$ times, so this is 
$\sum c_i(2c_i+1)$. Hence,
\[ K(2K+1)=\sum c_i(2c_i+1)=k(2K+1), \]
which implies $k=K$ as desired. $\blacksquare$
	
\end{document}
